Hybrid quantum-classical unsupervised data clustering based on the Self-Organizing Feature Map

### 2024-11-11 manuscript/main.tex
Update qcircuit figure with one for 4 qubits

\begin{figure}[t]
	\includegraphics[width=\columnwidth]{qcircuit.eps}
  \caption{%
		Quantum circuit for the quantum parallelized Hamming distance calculation between all pairs of binary vectors from two sets ${X}$ and ${Y}$.
		First, we encode information about pairwise different qubits in a quantum state of the $X$-register by applying the CNOT gates.
		Second, the Hamming distance values are extracted to the amplitudes of superposition with the control phase rotation (see Eq.~(\ref{eq:controled_phase_rotation})) and Hadamard gates.
		Finally, a quantum space of the $X$-register is returned to the initial basis for information retrieval.
	}
	\label{fig:qcircuit}
\end{figure}

>>>>

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{qcircuit.eps}
  \caption{%
    Example of quantum circuit for the quantum parallelized Hamming distance calculation between all pairs of 4-bit binary vectors from two sets ${X}$ and ${Y}$.
    First, we encode information about pairwise different qubits in a quantum state of the $X$-register by applying the CNOT gates.
    Second, the Hamming distance values are extracted to the amplitudes of superposition with the control phase rotation (see Eq.~(\ref{eq:controled_phase_rotation})) and Hadamard gates.
    Finally, a quantum space of the $X$-register is returned to the initial basis for information retrieval.
  }
  \label{fig:qcircuit}
\end{figure}
